A highly-available move operation for replicated trees and distributed filesystems

### 2020-05-22 paper/move-op.tex
Use italics for Isabelle code
Highlight "if/then/else" and "let/in" as keywords, and constructors in
roman font

\usepackage{lineno}
\usepackage{isabelle,isabellesym}
\isabellestyle{rm}
\renewenvironment{isabelle}{%
  \medbreak\indent%
  \renewcommand{\isanewline}{\\}%
  \begin{minipage}{\columnwidth}% use minipage to prevent page breaks
  \begin{isabellebody}%
  \begin{tabbing}%
}{%
  \end{tabbing}%
  \end{isabellebody}%
  \end{minipage}%
  \medbreak%
}
\renewcommand{\isacartoucheopen}{}
\renewcommand{\isacartoucheclose}{}

@@

\ \ {\isacharequal}\ Move\ {\isacharparenleft}move{\isacharunderscore}time{\isacharcolon}\ {\isacharprime}t{\isacharparenright}\isanewline

@@

\ \ {\isacharequal}\ LogMove\ {\isacharparenleft}log{\isacharunderscore}time{\isacharcolon}\ {\isacharprime}t{\isacharparenright}\isanewline

@@

\ \ \ \ \ if\ {\isasymexists}{\isacharbang}parent{\isachardot}\ {\isasymexists}{\isacharbang}meta{\isachardot}\ {\isacharparenleft}parent{\isacharcomma}\ meta{\isacharcomma}\ child{\isacharparenright}\ {\isasymin}\ tree\ then\isanewline
\ \ \ \ \ \ \ Some\ {\isacharparenleft}THE\ {\isacharparenleft}parent{\isacharcomma}\ meta{\isacharparenright}{\isachardot}\ {\isacharparenleft}parent{\isacharcomma}\ meta{\isacharcomma}\ child{\isacharparenright}\ {\isasymin}\ tree{\isacharparenright}\isanewline
\ \ \ \ \ else\ None{\isacartoucheclose}\isanewline

@@

\ \ {\isacartoucheopen}do{\isacharunderscore}op\ {\isacharparenleft}Move\ t\ newp\ m\ c{\isacharcomma}\ tree{\isacharparenright}\ {\isacharequal}\isanewline
\ \ \ \ \ {\isacharparenleft}LogMove\ t\ {\isacharparenleft}get{\isacharunderscore}parent\ tree\ c{\isacharparenright}\ newp\ m\ c{\isacharcomma}\isanewline
\ \ \ \ \ \ if\ ancestor\ tree\ c\ newp\ {\isasymor}\ c\ {\isacharequal}\ newp\ then\ tree\isanewline
\ \ \ \ \ \ else\ {\isacharbraceleft}{\isacharparenleft}p{\isacharprime}{\isacharcomma}\ m{\isacharprime}{\isacharcomma}\ c{\isacharprime}{\isacharparenright}\ {\isasymin}\ tree{\isachardot}\ c{\isacharprime}\ {\isasymnoteq}\ c{\isacharbraceright}\ {\isasymunion}\ {\isacharbraceleft}{\isacharparenleft}newp{\isacharcomma}\ m{\isacharcomma}\ c{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isacartoucheclose}\isanewline

@@

\ \ {\isacartoucheopen}undo{\isacharunderscore}op\ {\isacharparenleft}LogMove\ t\ None\ newp\ m\ c{\isacharcomma}\ tree{\isacharparenright}\ {\isacharequal}\ {\isacharbraceleft}{\isacharparenleft}p{\isacharprime}{\isacharcomma}\ m{\isacharprime}{\isacharcomma}\ c{\isacharprime}{\isacharparenright}\ {\isasymin}\ tree{\isachardot}\ c{\isacharprime}\ {\isasymnoteq}\ c{\isacharbraceright}{\isacartoucheclose}\ {\isacharbar}\isanewline
\ \ {\isacartoucheopen}undo{\isacharunderscore}op\ {\isacharparenleft}LogMove\ t\ {\isacharparenleft}Some\ {\isacharparenleft}oldp{\isacharcomma}\ oldm{\isacharparenright}{\isacharparenright}\ newp\ m\ c{\isacharcomma}\ tree{\isacharparenright}\ {\isacharequal}\isanewline

@@

\ \ {\isacartoucheopen}redo{\isacharunderscore}op\ {\isacharparenleft}LogMove\ t\ {\isacharunderscore}\ p\ m\ c{\isacharparenright}\ {\isacharparenleft}ops{\isacharcomma}\ tree{\isacharparenright}\ {\isacharequal}\isanewline
\ \ \ \ \ {\isacharparenleft}let\ {\isacharparenleft}op{\isadigit{2}}{\isacharcomma}\ tree{\isadigit{2}}{\isacharparenright}\ {\isacharequal}\ do{\isacharunderscore}op\ {\isacharparenleft}Move\ t\ p\ m\ c{\isacharcomma}\ tree{\isacharparenright}\isanewline
\ \ \ \ \ \ in\ {\isacharparenleft}op{\isadigit{2}}\ {\isacharhash}\ ops{\isacharcomma}\ tree{\isadigit{2}}{\isacharparenright}{\isacharparenright}{\isacartoucheclose}\isanewline

@@

\ \ \ \ \ {\isacharparenleft}let\ {\isacharparenleft}op{\isadigit{2}}{\isacharcomma}\ tree{\isadigit{2}}{\isacharparenright}\ {\isacharequal}\ do{\isacharunderscore}op\ {\isacharparenleft}op{\isadigit{1}}{\isacharcomma}\ tree{\isadigit{1}}{\isacharparenright}\isanewline
\ \ \ \ \ \ in\ {\isacharparenleft}{\isacharbrackleft}op{\isadigit{2}}{\isacharbrackright}{\isacharcomma}\ tree{\isadigit{2}}{\isacharparenright}{\isacharparenright}{\isacartoucheclose}\ {\isacharbar}\isanewline

@@

\ \ \ \ \ {\isacharparenleft}if\ move{\isacharunderscore}time\ op{\isadigit{1}}\ {\isacharless}\ log{\isacharunderscore}time\ logop\isanewline
\ \ \ \ \ \ then\ redo{\isacharunderscore}op\ logop\ {\isacharparenleft}apply{\isacharunderscore}op\ op{\isadigit{1}}\ {\isacharparenleft}ops{\isacharcomma}\ undo{\isacharunderscore}op\ {\isacharparenleft}logop{\isacharcomma}\ tree{\isadigit{1}}{\isacharparenright}{\isacharparenright}{\isacharparenright}\isanewline
\ \ \ \ \ \ else\ let\ {\isacharparenleft}op{\isadigit{2}}{\isacharcomma}\ tree{\isadigit{2}}{\isacharparenright}\ {\isacharequal}\ do{\isacharunderscore}op\ {\isacharparenleft}op{\isadigit{1}}{\isacharcomma}\ tree{\isadigit{1}}{\isacharparenright}\ in\ {\isacharparenleft}op{\isadigit{2}}\ {\isacharhash}\ logop\ {\isacharhash}\ ops{\isacharcomma}\ tree{\isadigit{2}}{\isacharparenright}{\isacharparenright}{\isacartoucheclose}\isanewline

>>>>

\usepackage{lineno}
\usepackage{isabelle,isabellesym}
\isabellestyle{it}
\renewenvironment{isabelle}{%
  \medbreak\indent%
  \renewcommand{\isanewline}{\\}%
  \begin{minipage}{\columnwidth}% use minipage to prevent page breaks
  \begin{isabellebody}%
  \begin{tabbing}%
}{%
  \end{tabbing}%
  \end{isabellebody}%
  \end{minipage}%
  \medbreak%
}
\renewcommand{\isacartoucheopen}{}
\renewcommand{\isacartoucheclose}{}

@@

\ \ {\isacharequal}\ {\rm Move}\ {\isacharparenleft}move{\isacharunderscore}time{\isacharcolon}\ {\isacharprime}t{\isacharparenright}\isanewline

@@

\ \ {\isacharequal}\ {\rm LogMove}\ {\isacharparenleft}log{\isacharunderscore}time{\isacharcolon}\ {\isacharprime}t{\isacharparenright}\isanewline

@@

\ \ \ \ \ \isacommand{if}\ {\isasymexists}{\isacharbang}parent{\isachardot}\ {\isasymexists}{\isacharbang}meta{\isachardot}\ {\isacharparenleft}parent{\isacharcomma}\ meta{\isacharcomma}\ child{\isacharparenright}\ {\isasymin}\ tree\ \isacommand{then}\isanewline
\ \ \ \ \ \ \ {\rm Some}\ {\isacharparenleft}{\rm THE}\ {\isacharparenleft}parent{\isacharcomma}\ meta{\isacharparenright}{\isachardot}\ {\isacharparenleft}parent{\isacharcomma}\ meta{\isacharcomma}\ child{\isacharparenright}\ {\isasymin}\ tree{\isacharparenright}\isanewline
\ \ \ \ \ \isacommand{else}\ {\rm None}{\isacartoucheclose}\isanewline

@@

\ \ {\isacartoucheopen}do{\isacharunderscore}op\ {\isacharparenleft}{\rm Move}\ t\ newp\ m\ c{\isacharcomma}\ tree{\isacharparenright}\ {\isacharequal}\isanewline
\ \ \ \ \ {\isacharparenleft}{\rm LogMove}\ t\ {\isacharparenleft}get{\isacharunderscore}parent\ tree\ c{\isacharparenright}\ newp\ m\ c{\isacharcomma}\isanewline
\ \ \ \ \ \ \isacommand{if}\ ancestor\ tree\ c\ newp\ {\isasymor}\ c\ {\isacharequal}\ newp\ \isacommand{then}\ tree\isanewline
\ \ \ \ \ \ \isacommand{else}\ {\isacharbraceleft}{\isacharparenleft}p{\isacharprime}{\isacharcomma}\ m{\isacharprime}{\isacharcomma}\ c{\isacharprime}{\isacharparenright}\ {\isasymin}\ tree{\isachardot}\ c{\isacharprime}\ {\isasymnoteq}\ c{\isacharbraceright}\ {\isasymunion}\ {\isacharbraceleft}{\isacharparenleft}newp{\isacharcomma}\ m{\isacharcomma}\ c{\isacharparenright}{\isacharbraceright}{\isacharparenright}{\isacartoucheclose}\isanewline

@@

    \ \ {\isacartoucheopen}undo{\isacharunderscore}op\ {\isacharparenleft}{\rm LogMove}\ t\ {\rm None}\ newp\ m\ c{\isacharcomma}\ tree{\isacharparenright}\ {\isacharequal}\ {\isacharbraceleft}{\isacharparenleft}p{\isacharprime}{\isacharcomma}\ m{\isacharprime}{\isacharcomma}\ c{\isacharprime}{\isacharparenright}\ {\isasymin}\ tree{\isachardot}\ c{\isacharprime}\ {\isasymnoteq}\ c{\isacharbraceright}{\isacartoucheclose}\ {\isacharbar}\isanewline
\ \ {\isacartoucheopen}undo{\isacharunderscore}op\ {\isacharparenleft}{\rm LogMove}\ t\ {\isacharparenleft}{\rm Some}\ {\isacharparenleft}oldp{\isacharcomma}\ oldm{\isacharparenright}{\isacharparenright}\ newp\ m\ c{\isacharcomma}\ tree{\isacharparenright}\ {\isacharequal}\isanewline

@@

\ \ {\isacartoucheopen}redo{\isacharunderscore}op\ {\isacharparenleft}{\rm LogMove}\ t\ {\isacharunderscore}\ p\ m\ c{\isacharparenright}\ {\isacharparenleft}ops{\isacharcomma}\ tree{\isacharparenright}\ {\isacharequal}\isanewline
\ \ \ \ \ {\isacharparenleft}\isacommand{let}\ {\isacharparenleft}op{\isadigit{2}}{\isacharcomma}\ tree{\isadigit{2}}{\isacharparenright}\ {\isacharequal}\ do{\isacharunderscore}op\ {\isacharparenleft}{\rm Move}\ t\ p\ m\ c{\isacharcomma}\ tree{\isacharparenright}\isanewline
\ \ \ \ \ \ \isacommand{in}\ {\isacharparenleft}op{\isadigit{2}}\ {\isacharhash}\ ops{\isacharcomma}\ tree{\isadigit{2}}{\isacharparenright}{\isacharparenright}{\isacartoucheclose}\isanewline

@@

\ \ \ \ \ {\isacharparenleft}\isacommand{let}\ {\isacharparenleft}op{\isadigit{2}}{\isacharcomma}\ tree{\isadigit{2}}{\isacharparenright}\ {\isacharequal}\ do{\isacharunderscore}op\ {\isacharparenleft}op{\isadigit{1}}{\isacharcomma}\ tree{\isadigit{1}}{\isacharparenright}\isanewline
\ \ \ \ \ \ \isacommand{in}\ {\isacharparenleft}{\isacharbrackleft}op{\isadigit{2}}{\isacharbrackright}{\isacharcomma}\ tree{\isadigit{2}}{\isacharparenright}{\isacharparenright}{\isacartoucheclose}\ {\isacharbar}\isanewline

@@

\ \ \ \ \ {\isacharparenleft}\isacommand{if}\ move{\isacharunderscore}time\ op{\isadigit{1}}\ {\isacharless}\ log{\isacharunderscore}time\ logop\isanewline
\ \ \ \ \ \ \isacommand{then}\ redo{\isacharunderscore}op\ logop\ {\isacharparenleft}apply{\isacharunderscore}op\ op{\isadigit{1}}\ {\isacharparenleft}ops{\isacharcomma}\ undo{\isacharunderscore}op\ {\isacharparenleft}logop{\isacharcomma}\ tree{\isadigit{1}}{\isacharparenright}{\isacharparenright}{\isacharparenright}\isanewline
\ \ \ \ \ \ \isacommand{else}\ \isacommand{let}\ {\isacharparenleft}op{\isadigit{2}}{\isacharcomma}\ tree{\isadigit{2}}{\isacharparenright}\ {\isacharequal}\ do{\isacharunderscore}op\ {\isacharparenleft}op{\isadigit{1}}{\isacharcomma}\ tree{\isadigit{1}}{\isacharparenright}\ \isacommand{in}\ {\isacharparenleft}op{\isadigit{2}}\ {\isacharhash}\ logop\ {\isacharhash}\ ops{\isacharcomma}\ tree{\isadigit{2}}{\isacharparenright}{\isacharparenright}{\isacartoucheclose}\isanewline
